Corpus

### 2021-04-06 analysis/corpus.Rmd
Fix corpus stats

```{r load corpus}
PKG_S <- 
  read_fst(PACKAGE_SUM_CALLS_FILE) %>%
  # remove evals that are inside the scripts,
  # for PKG_C we are only interested in evals in packages
  filter(!str_starts(eval_call_srcref, "::global::main")) %>% 
  as_tibble()

PKG_evals_per_package <- 
  count(PKG_S, caller_package, eval_call_srcref) %>%
  count(caller_package) %>% 
  rename(
    package=caller_package, 
    evals_hit=n
  )

@@

PKG_C <- 
  CRAN_C %>%
  filter(in_corpus, package_code > 0) %>%
  left_join(PKG_evals_per_package, by="package") %>% 
  mutate(
    evals_hit=as.integer(evals_hit),
    # this is the case when there is eval in package loading code
    # this we will always run
    evals_hit=if_else(evals_hit > evals, evals, evals_hit),
    evals_coverage=evals_hit/evals
  ) %>% 
  mutate_if(is.numeric, replace_na, 0) %>%
  as_tibble()

CRAN_E <- 
  read_csv(PACKAGE_EVALS_STATIC_FILE) %>% 
  # TODO: There are very few NA, plus when srcref is NA, the rest of the row in NA
  # we should look at this
  filter(!is.na(srcref))

@@

KAGGLE_ALL <- local({
  kernels <- read_csv(KAGGLE_KERNEL_FILE)
  evals <- read_csv(KAGGLE_EVALS_STATIC_FILE) %>% count(package) %>% rename(evals=n)
  left_join(kernels, evals, by="package") 
}) %>%
  mutate_if(is.numeric, replace_na, 0) %>% 
  mutate(evals=as.integer(evals)) %>% 
  as_tibble()

>>>>

```{r load corpus}
PKG_S <- 
  read_fst(PACKAGE_SUM_CALLS_FILE) %>%
  as_tibble()

PKG_evals_per_package <- 
  PKG_S %>%
  group_by(eval_source) %>% 
  summarise(
    evals_hit=n_distinct(eval_call_srcref)
  ) %>%
  rename(
    package=eval_source
  )

@@

PKG_C <- 
  CRAN_C %>%
  filter(in_corpus) %>%
  left_join(PKG_evals_per_package, by="package") %>% 
  mutate_if(is.numeric, replace_na, 0) %>%
  mutate(
    evals_hit=as.integer(evals_hit),
    # this is because some evals are defined in functions that are stored in environments (asserthat/base.r)
    # or lists
    evals=ifelse(evals < evals_hit, evals_hit, evals),
    evals_coverage=evals_hit/evals
  ) %>% 
  as_tibble()

CRAN_E <- 
  read_csv(
    PACKAGE_EVALS_STATIC_FILE,
    col_types=cols(
      package = col_character(),
      fun_name = col_character(),
      srcref = col_character(),
      call_fun_name = col_character(),
      args = col_character()
    )
  ) %>% 
  # TODO: There are very few NA, plus when srcref is NA, the rest of the row in NA
  # we should look at this
  filter(!is.na(srcref))

@@

KAGGLE_ALL <- local({
  kernels <- read_csv(
    KAGGLE_KERNEL_FILE,
    col_types = cols(
      package = col_character(),
      file = col_character(),
      id = col_character(),
      language = col_character(),
      kernel_type = col_character(),
      competition = col_character(),
      blank = col_double(),
      comment = col_double(),
      code = col_double(),
      hash = col_character()
    )
  )
  evals <- read_csv(
    KAGGLE_EVALS_STATIC_FILE,
    col_types = cols(
      package = col_character(),
      fun_name = col_character(),
      srcref = col_character(),
      call_fun_name = col_character(),
      args = col_character()
    )
  ) %>% 
    count(package) %>% 
    rename(evals=n)
  left_join(kernels, evals, by="package") 
}) %>%
  mutate_if(is.numeric, replace_na, 0) %>% 
  mutate(evals=as.integer(evals)) %>% 
  as_tibble()
